\documentclass{article}
\usepackage[english]{babel}
\usepackage{textcmds}
\usepackage{csquotes}
\usepackage{comment}
\usepackage{float}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage[style=authoryear,
backend=biber,
giveninits=true,
uniquelist = false,
uniquename=init,
isbn=false,
maxcitenames=2,
dashed=false,
maxbibnames=999,
doi=false,
url=false]{biblatex}
\addbibresource{bibliography.bib}
%--------------------------------------------------------------
%
% HERE IS WHERE THE DOCUMENT STARTS!
%
%--------------------------------------------------------------
\begin{document}
\subsection*{Homework Assignment 2}
\begin{enumerate}
  \item A firm is using two inputs, \(x_1\) and \(x_2\), to produce one output, \(y\). The input prices are \(w_1\) and \(w_2\), respectively. The price of \(x_1\) (\(w_1\)) has increased, while \(w_2\) has remained unchanged. The firm has responded to this by changing how much of each input it uses without altering the quantity of its output.
  \begin{enumerate}
    \item What has happened to the firm’s use of \(x_1\) and \(x_2\)? Show your answer graphically.
    \item Have the overall costs of the firm gone up or down?
  \end{enumerate}
  \item Show who bears the burden of an excise tax in the short run and long run. Is the tax burden borne by the consumer or the producer, or by both?
  \item Taxi licenses and public transport: discuss the implications of expanding public transport network on the cost of taxi licenses.
  \item Patents offer inventors a temporary monopoly and thus allow then to enjoy higher profits than in a competitive environment while the patent lasts. This allows them to sell their products well above the marginal cost. It has been argued that in the case of life-saving medications (for example antiviral drugs against AIDS), the patent protection should be short-lived or none so that the medicines can be distributed cheaply, especially in less developed countries. Discuss.
\end{enumerate}
\nocite{Valrian_Inter_Micro}
\printbibliography

\end{document}
