\documentclass{article}
\usepackage[english]{babel}
\usepackage{textcmds}
\usepackage{csquotes}
\usepackage{comment}
\usepackage{float}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage[style=authoryear,
backend=biber,
giveninits=true,
uniquelist = false,
uniquename=init,
isbn=false,
maxcitenames=2,
dashed=false,
maxbibnames=999,
doi=false,
url=false]{biblatex}
\addbibresource{bibliography.bib}
%--------------------------------------------------------------
%
% HERE IS WHERE THE DOCUMENT STARTS!
%
%--------------------------------------------------------------
\begin{document}

This problem set is based on  \cite{Valrian_Inter_Micro}

\subsubsection*{Problem 9: Monopoly Behaviour }
 Let us retake the taquer\'ia problem from last problem set.
 Let us first focus on the short run and suppose that the
 production function is
\begin{equation*}
  y = h(l) = cl^{1-\alpha}
\end{equation*}

\begin{itemize}
  \item If \(\alpha =0\), what type of technology is this? What is the taquer\'ia's
  profit maximization problem? What is the minimum taco price for which
  the taquer\'ia is willing to not shutdown? Discuss why.
  \item Suppose we are now talking about the long run. What other condition can we impose to
  give the problem more \qq{structure}?
  \item Now suppose \(\alpha = \frac{1}{2}\). What type of technology is this? Solve
  the taquer\'ia's optimization problem. What is the condition the optimal level
  of output solves?
  \item Now suppose that this is the only taquer\'ia in town. The town's taco demand
  is given by the inverse demand function \(Q_d(p) = a-bp\). How is the taquer\'ia's
  optimization problem affected? Is the equilibrium affected? If so, how? Show your
  answer graphically.
\end{itemize}
\newpage

\printbibliography

\end{document}
